---
title: "Quiz zum Fach Digitaltechnik"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(shiny)
library(learnr)
library(reticulate)
use_condaenv("rstudio")
knitr::opts_chunk$set(echo = FALSE)
```

# Grundlegendes

Dies ist eine kleines Quiz welches für das Fach Digitaltechnik an der ABB Technikerschule in Baden erstellt wurde.
Im folgenden werden Sie, unterteilt in thematische Kapitel, mit verschiedenen Fragestellungen aus dem Bereich der Digitaltechnik konfrontiert. Ziel sollte es sein Ihr Wissen über die Digitaltechnik weiter zu festigen.

## Einführung

In diesem Kapitel werden grundlegende Themen der Digitaltechnik behandelt.

```{r quiz-K1}
quiz(
  question("In welchen Bereichen wird auf Digitaltechnik zurückgegriffen?",correct = "Richtig!", incorrect = "Falsch!",submit_button = "Senden", try_again_button = "Wiederholen", allow_retry = TRUE, random_answer_order = TRUE,
    answer("Computertechnik", correct = TRUE),
    answer("Nachrichten- und Kommunikationstechnik", correct=TRUE),
    answer("Automatisierungstechnik", correct = TRUE),
    answer("Messtechnik", correct = TRUE) 
  ),
  question("In der Digitaltechnik wird zwischen zwei logischen Zuständen unterschieden!",correct = "Richtig!", incorrect = "Falsch!",submit_button = "Senden", try_again_button = "Wiederholen", allow_retry = TRUE, random_answer_order = TRUE,
    answer("Wahr", correct = TRUE),
    answer("Falsch")
  ),
  question("Digital ist grundsätzlich besser als analog!",correct = "Richtig!", incorrect = "Falsch!",submit_button = "Senden", try_again_button = "Wiederholen", allow_retry = TRUE, random_answer_order = TRUE,
    answer("Falsch", correct = TRUE),
    answer("Richtig.")
  ),
  question("Digitaltechnik wird die Analogtechnik in Zukunft völlig verdrängen!",correct = "Richtig!", incorrect = "Falsch!",submit_button = "Senden", try_again_button = "Wiederholen", allow_retry = TRUE, random_answer_order = TRUE,
    answer("Falsch", correct = TRUE),
    answer("Richtig.")
  )
)
```

## Grundbegriffe und Grundelemente

```{r quiz-K2}
quiz(
  question("Analoge Grössen können innerhalb eines zulässigen Bereichs jeden denkbaren Wert annehmen!",correct = "Richtig!", incorrect = "Falsch!",submit_button = "Senden", try_again_button = "Wiederholen", allow_retry = TRUE, random_answer_order = TRUE,
    answer("Richtig", correct = TRUE),
    answer("Falsch")
  ),
  question("In der Digitaltechnik wird zwischen zwei logischen Zuständen unterschieden!",correct = "Richtig!", incorrect = "Falsch!",submit_button = "Senden", try_again_button = "Wiederholen", allow_retry = TRUE, random_answer_order = TRUE,
    answer("Wahr", correct = TRUE),
    answer("Falsch")
  ),
  question("Welche der folgenden Aussagen sind auf eine digitale Grössendarstellung zutreffend?",correct = "Richtig!", incorrect = "Falsch!",submit_button = "Senden", try_again_button = "Wiederholen", allow_retry = TRUE, random_answer_order = TRUE,
    answer("Verwendet endliche Anzahl von Elemente zurück.", correct = TRUE),
    answer("Der Genauigkeit ist eine physikalische Grenze gesetzt."),
    answer("Digitale Anzeigen sind nicht eindeutig.")
  ),
  question("Digitaltechnik muss zwingend aus zwei Elementen/Zuständen bestehen!",correct = "Richtig!", incorrect = "Falsch!",submit_button = "Senden", try_again_button = "Wiederholen", allow_retry = TRUE, random_answer_order = TRUE,
    answer("Falsch", correct = TRUE),
    answer("Richtig.")
  )
)
```

Folgende mathematische Formeln existieren:

$$
x=a+b^{2}
$$

### Exercise 

*Here's a simple exercise with an empty code chunk provided for entering the answer.*

Python Code funktioniert. Schreibe eine Funktion die den Text "Hello World" auf der Konsole ausgibt!

```{python print, echo=TRUE}
cars = ["Volvo","Audi","BMW"]
for i in cars:
  print(i)

```

Write the R code required to add two plus two:

```{r two-plus-two, exercise=TRUE}

```

```{chunck codetest, echo=TRUE}
sudo su - -c "R -e \"install.packages(c('ggplot2', 'dplyr', 'tidyr', 'readr', 'lazyeval', 'stringr', 'ggthemes', 'ggExtra', 'magrittr', 'viridis', 'gridExtra', 'lubridate', 'fasttime', 'data.table'), repos='http://cran.rstudio.com/')\""
```

### Exercise with Code

*Here's an exercise with some prepopulated code as well as `exercise.lines = 5` to provide a bit more initial room to work.*

Now write a function that adds any two numbers and then call it:

```{r add-function, exercise=TRUE, exercise.lines = 5}
add <- function() {
  
}
```

## Topic 2

### Exercise with Hint

*Here's an exercise where the chunk is pre-evaulated via the `exercise.eval` option (so the user can see the default output we'd like them to customize). We also add a "hint" to the correct solution via the chunk immediate below labeled `print-limit-hint`.*

Modify the following code to limit the number of rows printed to 5:

```{r print-limit, exercise=TRUE, exercise.eval=TRUE}
mtcars
```

```{r print-limit-hint}
head(mtcars)
```

### Quiz

*You can include any number of single or multiple choice questions as a quiz. Use the `question` function to define a question and the `quiz` function for grouping multiple questions together.*

Some questions to verify that you understand the purposes of various base and recommended R packages:

```{r quiz}
quiz(
  question("Which package contains functions for installing other R packages?",
    answer("base"),
    answer("tools"),
    answer("utils", correct = TRUE),
    answer("codetools")
  ),
  question("Which of the R packages listed below are used to create plots?",
    answer("lattice", correct = TRUE),
    answer("tools"),
    answer("stats"),
    answer("grid", correct = TRUE)
  )
)
```

